A general and efficient representation of Ancestral Recombination Graphs

### 2023-10-06 paper.tex
Make Fig 3 fit on half a page

\begin{figure}
\centering
% TODO update the source of this figure to make less tall. It's taking
% up far too much vspace at in native coords at the moment.
\includegraphics[width=0.6\textwidth]{illustrations/ancestry-resolution}
\caption{\label{fig-ancestry-resolution}
Converting the \citet[][Fig.~1]{wiuf1999recombination} example graph
to a gARG. (A) The original eARG; square nodes represent events, with
each recombination (red) showing the corresponding breakpoint.
(B) The corresponding gARG with breakpoints directly converted to
edges annotated with inheritance intervals.
(C) The sample-resolved gARG resulting from simplifying with respect
to the samples, \noderef{a}, \noderef{b}, and \noderef{c}.
Dashed lines show edges that are
no longer present (in practice, nodes \noderef{g} and \noderef{q} would also be removed).
Coalescence with respect to the sample is indicated by shaded bars, as
in Fig~\ref{fig-arg-in-pedigree}A.
Line thickness is proportional to the genomic span of each edge.
Nodes representing recombination events have been retained
for clarity, but could be removed by simplification if
desired.
}
\end{figure}

>>>>

\begin{figure}
\centering
% TODO update the source of this figure to make less tall. It's taking
% up far too much vspace at in native coords at the moment.
\includegraphics[width=\textwidth]{illustrations/ancestry-resolution}
\caption{\label{fig-ancestry-resolution}
Converting the \citet[][Fig.~1]{wiuf1999recombination} example
to a gARG. (A) The original eARG; square nodes represent events, with
each recombination (red) containing a breakpoint.
(B) The corresponding gARG with breakpoints directly converted to
edges annotated with inheritance intervals.
(C) The sample-resolved gARG resulting from simplifying with respect
to the samples, \noderef{a}, \noderef{b}, and \noderef{c}.
Dashed lines show edges that are
no longer present (in practice, nodes \noderef{g}, \noderef{j}, and \noderef{q} would also be removed).
Coalescence with respect to the sample is indicated by shaded bars, as
in Fig~\ref{fig-arg-in-pedigree}A.
Line thickness is proportional to the genomic span of each edge.
Nodes representing recombination events are retained
for clarity, but could be removed by simplification if
desired.
}
\end{figure}
